A seamless, client-centric programming model for type safe web applications

### 2014-06-19 paper.tex
Be clearer about why server-side state is wrapped in the Server monad.
Be more explicit about result MVars.

An \lstinline!MVar! is associated with the
connecting client's session identifier, and the pair is prepended to the
recipient list. Notice how the application's server state is passed in as the
function's argument.

@@

\begin{code}
type Nonce = Int
type Client = StateT Nonce Conc
\end{code}

@@

\begin{code}
onServer :: Serialize a
         => Remote (Server a) -> Client a
onServer (Remote identifier args) = do
  nonce <- get
  put (nonce + 1)
  mv <- createResultMVar nonce
  webSocketSend $
    toJSON (nonce, identifier, reverse args)  
  takeMVar mv
\end{code}

@@

\begin{code}
onMessage :: JSON -> Client ()
onMessage response = do
  let (nonce, result) = fromJSON response
  mv <- findResultMVar nonce
  putMVar mv result
\end{code}

>>>>

An \lstinline!MVar! is associated with the
connecting client's session identifier, and the pair is prepended to the
recipient list. Notice how the application's server state is passed in as the
function's argument, wrapped in the \lstinline!Server! monad in order to
prevent client-side inspection.

@@

\begin{code}
type Nonce = Int
type ClientState = (Nonce, Map Nonce (MVar JSON))
type Client = StateT ClientState Conc
\end{code}

@@

\begin{code}
newResult :: Client (Nonce, MVar JSON)
newResult = do
  (nonce, m) <- get
  mv <- liftIO newEmptyMVar
  put (nonce+1, insert nonce var m)
  return (nonce, mv)

onServer :: Serialize a
         => Remote (Server a) -> Client a
onServer (Remote identifier args) = do
  (nonce, mv) <- newResult
  webSocketSend $
    toJSON (nonce, identifier, reverse args)  
  fromJSON <$> takeMVar mv
\end{code}

The \lstinline!createResultMVar! function creates a new \lstinline!MVar!,
paired with its corresponding nonce in the

@@

\begin{code}
onMessage :: JSON -> Client ()
onMessage response = do
  let (nonce, result) = fromJSON response
  (n, m) <- get
  put (n, delete nonce m)
  putMVar (m ! nonce) result
\end{code}
